Sketching for Density Estimation

### 2018-11-14 density.tex
before merge

Let us consider a signed sum of error function $E(q) = \sum_{i=1}^{n} s_i f(x_i,q)$.
Now consider $\tilde F(q) = F(q) + E(q) = \sum_{i=1}^{n} f(x_i,q)  + \sum_{i=1}^{n} s_i f(x_i,q)  = 2 \sum_{i | s_i=1} f(x_i,q)$.
Therefore $\tilde F(q)$ is a coreset for $F(q)$ with item weights of $2$ and error at most $|\tilde F(q) - F(q)| \le \max_q | E(q)|$.
Note that the above is true for any choice of signs $s_i$, specifically, for those minimizing $\max_q | E(q)|$.
We call $E$ flat if $\min_s \max_q |E(q)| = o(n)$.

>>>>

Let us consider a signed sum of error function $E(q) = \sum_{i=1}^{n} s_i f(x_i,q)$.
Now consider $\tilde F(q) = F(q) + \Delta(q) = \sum_{i=1}^{n} f(x_i,q)  + \sum_{i=1}^{n} s_i f(x_i,q)  = 2 \sum_{i | s_i=1} f(x_i,q)$.
Therefore $\tilde F(q)$ is a coreset for $F(q)$ with item weights of $2$ and error at most $|\tilde F(q) - F(q)| \le \max_q | \Delta(q)|$.
Note that the above is true for any choice of signs $s_i$, specifically, for those minimizing $\max_q | \Delta(q)|$.
We call $E$ flat if $\min_s \max_q |\Delta(q)| = o(n)$.
